---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# cloudfil

<!-- badges: start -->
<!-- badges: end -->

The goal of `cloudfil` is to fill the gaps in satellite images caused by clouds.

# Installation

The package can be installed from Github as follows:

```{r eval=FALSE}
library("devtools")
install_github("mmontesinosanmartin/cloudfil")
```

# Example

This is an example on how to fill gaps in satellite images left by clouds. The technique requires the cloudy image and a clear-sky image from the same location on another date.

```{r dataset}
library(cloudfil)
data("clr.img")
data("cld.img")
plotRGB(cld.img, stretch = "lin")
```

Apply the `fill_stack()` function to fill the `cld.img` based on the `clr.img`. Define a neighborhood of size (2w+1)x(2w+1) around every missing pixel. The information in the neighboring area is used to fill the missing value.

```{r filling}
fill.img <- fill_stack(clr.img, cld.img, w = 100)
plotRGB(fill.img$img, stretch = "lin")
```

Let's test the prediction against the actual image:

```{r evaluating}
data("trg.img")
eval_rmse(fill.img$img, trg.img)
plot(fill.img$flag)
```

